\input{config/document-setup}

\begin{document}
\lecture{Introduction}{January 11, 2018}{Dev Dabke}

\section{Logistics}\label{sec:logistics}

\begin{info}[Contact Information]{info:contact}
    \begin{itemize}
        \item Email address: \href{mailto:dv@math.duke.edu}{dv@math.duke.edu}
        \item Office Hours: To Be Determine, By Appointment
        \item Course Slack: \href{cattheory.slack.com}{cattheory.slack.com}
    \end{itemize}
\end{info}

\begin{info}[Course Structure]{info:structure}
    \begin{itemize}
        \item 50\% of grade: \( \approx 7 \) problem sets in \LaTeX
        \item 1 course project
        \item Some use of Haskell
    \end{itemize}
\end{info}

\section{Basic Definitions}\label{sec:definitions}

We will take the definition of a set for granted and we will assume the use of naive set theory.
Additionally, we assume the notion of a function (or map) and the standard notation for an application of a function \( f(\ldots) \).

\begin{dfn}[Relation]{dfn:relation}
    On some set \( X \), a \textcolor{dfn-color}{binary relation} is a function \( \textcolor{dfn-color}{\sim} \) such that
    \[
        \sim \, : X \times X \to \mathbb{B}
    \]
    where \( \mathbb{B} = \{ \top, \bot \} \).
    Where \( x_1, x_2 \in X \), we write \( x_1 \sim x_2 \) to mean \( \sim(x_1, x_2) = \top \).
    \\ \\
    In other words, a relation is a ``binary'' or ``2-ary'' function (i.e.\ it takes two inputs) and returns either a true or false value (also notated as a \( 1 \) or \( 0 \)).
\end{dfn}

\begin{dfn}[Pre-Order]{dfn:pre-order}
    A \textcolor{dfn-color}{pre-order} \( (P, \textcolor{dfn-color}{\leq}) \) is a set \( P \) with a \hyperref[dfn:relation]{binary relation} \( \leq \) such that
    \begin{itemize}
        \item \( \forall x \in P, \, x \leq x \) (reflexivity)
        \item \( \forall x, y, z \in P, \, [x \leq y \text{ and } x \leq z] \implies x \leq z \) (transitivity)
    \end{itemize}
    We also say that \( x \) \textcolor{dfn-color}{precedes} \( y \) when \( x \leq y \).
    \\ \\
    If \( \leq \) satisfies the condition that
    \[
        \forall x, y \in P, \, [x \leq y \text{ and } y \leq x] \implies x = y
    \]
    then we say that \( P \) is a \textcolor{dfn-color}{partially ordered set}.
    \\ \\
    If \( \leq \) satisfies the condition that
    \[
        \forall x, y \in P, \, x \leq y \text{ or } y \leq x
    \]
    then we say that \( P \) is a \textcolor{dfn-color}{totally ordered set}.
\end{dfn}

\begin{eg}[Pre-Order with Power Sets]{eg:pre-order-power-sets}
    Let \( X = \{ a, b, c \} \), i.e.\ a set with elements \( a, b, c \).
    We say that its powerset \( \mathcal{P}_{X} \) consists of all subsets of \( X \) (which includes \( X \) itself and the empty set).
    We will construct the \hyperref[dfn:pre-order]{pre-order} \( (\mathcal{P}_{X}, \subseteq) \) of set inclusion.
    \\ \\
    Associated to this pre-order, we can draw the following diagram
    \\ \\
    \begin{tikzpicture}[node distance=2cm]
        \node (empty) {\( \emptyset \)};

        \node (b) [above of=empty] {\( \{ b \} \)};
        \node (a) [left of=b] {\( \{ a \} \)};
        \node (c) [right of=b] {\( \{ c \} \)};

        \node (ac) [above of=b] {\( \{ a, c \} \)};
        \node (ab) [left of=ac] {\( \{ a, b \} \)};
        \node (bc) [right of=ac] {\( \{ b, c \} \)};

        \node (abc) [above of=ac] {\( \{ a, b, c \} \)};

        \path[->,scale=3]
            (empty) edge node [above] {} (a)
            (empty) edge node [above] {} (b)
            (empty) edge node [above] {} (c)

            (a) edge node [above] {} (ab)
            (a) edge node [above] {} (ac)
            (b) edge node [above] {} (ab)
            (b) edge node [above] {} (bc)
            (c) edge node [above] {} (ac)
            (c) edge node [above] {} (bc)

            (ab) edge node [above] {} (abc)
            (ac) edge node [above] {} (abc)
            (bc) edge node [above] {} (abc)
        ;
    \end{tikzpicture}
    \\ \\
    where \( \longrightarrow \) denotes set inclusion.
    Importantly, we are only denoting some arrows.
    However, since the pre-order has the transitive property, we simply have to denote a ``covering'' set of \( \longrightarrow \), which we have done.
    In other words: all subset relationships are represented by \( \longrightarrow \) or some sequence of \( \longrightarrow \)s.
\end{eg}

\end{document}
